Reproducibility in plant pathology: where do we stand and a way forward

### 2022-04-08 analysis/paper/paper.Rmd
Add subtitles to figure 2 as per Reviewer 1's comments

rrpp <- import_notes()
theme_set(theme_classic())
A <- ggplot(rrpp, aes(y = as.factor(comp_mthds_avail))) +
  geom_bar(fill = "black") +
  ylab("Score") +
  xlab(NULL)

B <- ggplot(rrpp, aes(y = software_avail)) +
  geom_bar(fill = "black") +
  xlab(NULL) +
  ylab(NULL)

C <- ggplot(rrpp, aes(y = software_cite)) +
  geom_bar(fill = "black") +
  ylab("Score")

D <- ggplot(rrpp, aes(y = data_avail)) +
  geom_bar(fill = "black") +
  ylab(NULL)

>>>>

rrpp <- import_notes()
theme_set(theme_classic())
A <- ggplot(rrpp, aes(y = as.factor(comp_mthds_avail))) +
  geom_bar(fill = "black") +
  ylab("Score") +
  xlab(NULL) +
  ggtitle(label = "Computational methods availability")

B <- ggplot(rrpp, aes(y = software_avail)) +
  geom_bar(fill = "black") +
  xlab(NULL) +
  ylab(NULL) +
  ggtitle(label = "Software availability")

C <- ggplot(rrpp, aes(y = software_cite)) +
  geom_bar(fill = "black") +
  ylab("Score") +
  ggtitle(label = "Software citatations")

D <- ggplot(rrpp, aes(y = data_avail)) +
  geom_bar(fill = "black") +
  ylab(NULL) +
  ggtitle(label = "Data availability")
